---
title: Data Recoding
author: ''
date: '2022-02-23'
slug: data-recoding
categories: []
tags:
  - data recoding
---
## Load libraries
```{r}
library(tidyverse)
library(readxl)
url1 <- "C:\\Users\\CSUFTitan\\Downloads\\religious_income_data.xlsx"
rel_inc <- read_excel(url1)

```

```{r}
rel_inc %>%
  rename( 
    religion = `Religious tradition`, 
    n = `Sample Size` 
  )
```
### we want a new variable called income
```{r}
rel_inc %>%
  rename(
    religion = `Religious tradition`,
    n = `Sample Size`
  ) %>%
  pivot_longer( 
    cols = -c(religion, n),   # all but religion and n 
    names_to = "income",  
    values_to = "proportion" 
  )
```
### we want to calculate the frequency
```{r}
rel_inc %>%
  rename(
    religion = `Religious tradition`,
    n = `Sample Size`
  ) %>%
  pivot_longer(
    cols = -c(religion, n), 
    names_to = "income", 
    values_to = "proportion"
  ) %>%
  mutate(frequency = round(proportion * n))
```
### Save data
```{r}
rel_inc_long <- rel_inc %>% 
  rename(
    religion = `Religious tradition`,
    n = `Sample Size`
  ) %>%
  pivot_longer(
    cols = -c(religion, n), 
    names_to = "income", 
    values_to = "proportion"
  ) %>%
  mutate(frequency = round(proportion * n))
```
### We want to make a barplot
```{r}
ggplot(rel_inc_long, aes(y = religion, x = frequency)) +
  geom_col()
```
### We want to recode religion
```{r}
rel_inc_long <- rel_inc_long %>%
  mutate(religion = case_when(
    religion == "Evangelical Protestant"           ~ "Ev. Protestant",
    religion == "Historically Black Protestant"    ~ "Hist. Black Protestant",
    religion == 'Unaffiliated (religious "nones")' ~ "Unaffiliated",
    TRUE                                           ~ religion
  ))
```
### Plot recoded religion
```{r}
ggplot(rel_inc_long, aes(y = religion, x = frequency)) +
  geom_col()
```
### reverse religion color
```{r}
rel_inc_long <- rel_inc_long %>%
  mutate(religion = fct_rev(religion))
```
### Plot reversed religion color
```{r}
ggplot(rel_inc_long, aes(y = religion, x = frequency)) +
  geom_col()
```
### We want to add income
```{r}
ggplot(rel_inc_long, aes(y = religion, x = frequency, fill = income)) + 
  geom_col()
```
### We want to fill bars
```{r}
ggplot(rel_inc_long, aes(y = religion, x = frequency, fill = income)) +
  geom_col(position = "fill")
```
### We want to change the colors 
```{r}
ggplot(rel_inc_long, aes(y = religion, x = frequency, fill = income)) +
  geom_col(position = "fill") +
  scale_fill_viridis_d()
```
### We want to change the theme
```{r}
ggplot(rel_inc_long, aes(y = religion, x = frequency, fill = income)) +
  geom_col(position = "fill") +
  scale_fill_viridis_d() +
  theme_minimal()
```
### We want to move the legend to the bottom
```{r}
ggplot(rel_inc_long, aes(y = religion, x = frequency, fill = income)) +
  geom_col(position = "fill") +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(legend.position = "bottom")
```
### We want to adjust the legend
```{r}
ggplot(rel_inc_long, aes(y = religion, x = frequency, fill = income)) +
  geom_col(position = "fill") +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE))
```
### We want to fix the labels
```{r}
ggplot(rel_inc_long, aes(y = religion, x = frequency, fill = income)) +
  geom_col(position = "fill") +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
  labs(
    x = "Proportion", y = "", 
    title = "Income distribution by religious group", 
    subtitle = "Source: Pew Research Center, Religious Landscape Study", 
    fill = "Income" 
    )
```
