---
title: Data Types
author: ''
date: '2022-02-21'
slug: data-types
categories: []
tags:
  - data types
---
```{r}
library(tidyverse)
```
##Load Catlovers Data
```{r}
catlovers <- "https://raw.githubusercontent.com/rkavalakatt/tidyverse/main/cat-lovers.csv"
cat_lovers <- read_csv(catlovers)
```
## Running summarise fails due to non-numeric arguments
```{r}
cat_lovers %>%
 summarise(mean_cats = mean(number_of_cats))
```
### DOES NOT FIX ERROR, Using the help command on mean shows that there is an argument that takes out NA values

```{r}
?mean
cat_lovers %>%
  summarise(mean_cats = mean(number_of_cats, na.rm = TRUE))
```
## type command shows data type mismatch
```{r}
glimpse(cat_lovers)
```
### Recieved chr instead so we must explicitly convert the data type
```{r}
cat_lovers %>%
 mutate(number_of_cats = case_when(
     name == "Ginger Clark"  ~ 2,
     name == "Doug Bass"     ~ 3,
     TRUE                    ~as.numeric (number_of_cats)
    )) %>%
  summarise(mean_cats = mean(number_of_cats))
```
### Convert data types after manipulating data to the same type
```{r}
cat_lovers %>%
 mutate(number_of_cats = case_when(
     name == "Ginger Clark"  ~ "2",
     name == "Doug Bass"     ~ "3",
     TRUE                    ~ number_of_cats
    ),
number_of_cats =  as.numeric(number_of_cats)
) %>%
  summarise(mean_cats = mean(number_of_cats))
```
## Save value to catlovers
```{r}
cat_lovers <- cat_lovers %>%
 mutate(number_of_cats = case_when(
     name == "Ginger Clark"  ~ "2",
     name == "Doug Bass"     ~ "3",
     TRUE                    ~ number_of_cats
    ),
number_of_cats =  as.numeric(number_of_cats)
) %>%
  summarise(mean_cats = mean(number_of_cats))
```

