---
title: A1 Exercise
author: ''
date: '2022-03-21'
slug: a1-exercise
categories: []
tags: []
---

library(boot)
df <- read.csv(file = 'https://raw.githubusercontent.com/ellaprotz/webstie_ella/master/Real%20estate%20valuation%20data%20set.csv')
df
```

## Cross Validation
```{r}
set.seed(1)
head(df)
dim(df)
train <- sample(414, 207)
head(train)
```

```{r}
## Make the variables in Auto data set as locally accessible objects
attach(df)
lm.fit <- lm(Y.house.price.of.unit.area~X2.house.age, data = df, subset = train)
lm.fit
```

```{r}
mean((Y.house.price.of.unit.area - predict(lm.fit,df))[-train]^2)
```

```{r}
plot(Y.house.price.of.unit.area~X2.house.age)
```
```{r}
## Fit a quadratic function
lm.fit.poly <- lm(Y.house.price.of.unit.area~ poly(X2.house.age,2), data = df, subset = train)
lm.fit.poly
```
```{r}
## As we increase the degree of the polynomial to 2, the error decreases
mean((Y.house.price.of.unit.area - predict(lm.fit.poly,df))[-train]^2)
```

## LOOCV: Leave One Out and Cross Validation
```{r}
n = 2
set.seed(n)
train <- sample(414, 207)
attach(df)
lm.fit <- lm(Y.house.price.of.unit.area~X2.house.age, data = df, subset = train)
lm.fit.poly <- lm(Y.house.price.of.unit.area~ poly(X2.house.age,2), data = df, subset = train)
mean((Y.house.price.of.unit.area - predict(lm.fit,df))[-train]^2)
mean((Y.house.price.of.unit.area - predict(lm.fit.poly,df))[-train]^2)
```


```{r}
glm.fit <- glm(Y.house.price.of.unit.area~X2.house.age, data = df)
coef(glm.fit)
lm.fit <- lm(Y.house.price.of.unit.area~X2.house.age, data = df)
coef(lm.fit)
```
```{r}
cv.err <- cv.glm(df, glm.fit)
cv.err$delta
```
```{r}
cv.error <- rep(0,5)
degree <- 1:5
for (d in degree){
  glm.fit <- glm(Y.house.price.of.unit.area~poly(X2.house.age,d), data = df)
  cv.error[d] <- cv.glm(df, glm.fit)$delta[1]
}
cv.error
```
```{r}
plot(degree, cv.error, type = "b")
```

## K For Cross Validation
```{r}
K = 10
cv.error.10 <- rep(0,5)
degree <- 1:5
for (d in degree){
  glm.fit <- glm(Y.house.price.of.unit.area~poly(X2.house.age,d), data = df)
  cv.error.10[d] <- cv.glm(df, glm.fit, K = K)$delta[1]
}
cv.error.10
```
```{r}
plot(degree, cv.error, type = "b")
lines(degree, cv.error.10, type = "b", col = "red")
```
## Bootstrap Validation
```{r}
## Estimation of Accuracy of a Linear Model
boot.fn <- function(data, index) {
  return(coef(lm(Y.house.price.of.unit.area~X2.house.age, data = data, subset = index)))
}
```

```{r}
boot.fn(df, 1:414)
```

```{r}
boot(df, boot.fn, 100)
```


```{r}
boot.out <- boot(df, boot.fn, 100)
plot(boot.out)
```
```{r}
boot(df, boot.fn, 1000)
```

```{r}
boot.out <- boot(df, boot.fn, 1000)
plot(boot.out)
```

```{r}
boot(df, boot.fn, 10000)
```

```{r}
boot.out <- boot(df, boot.fn, 10000)
plot(boot.out)
```

