---
title: Data Classes
author: ''
date: '2022-02-21'
slug: data-classes
categories: []
tags: []
---
```{r}
library(tidyverse)
```

##Load catlovers
```{r}
catlovers <- "https://raw.githubusercontent.com/rkavalakatt/tidyverse/main/cat-lovers.csv"
cat_lovers <- read_csv(catlovers)
```

##Use glimpse on catlovers
```{r}
glimpse(cat_lovers)

```
##coerce when plotting
```{r}
ggplot(cat_lovers, mapping = aes(x = handedness)) +
  geom_bar()
```
##Use forcats to manipulate factors
```{r}
cat_lovers %>%
  mutate(handedness = fct_infreq(handedness)) %>%
  ggplot(mapping = aes(x = handedness)) +
  geom_bar()
```
##Load lubridate and hotel data
```{r}
library(lubridate)
hotel <- "https://raw.githubusercontent.com/rkavalakatt/tidyverse/main/hotels.csv"
hotels <- read_csv(hotel)

```
##Calculate and visualise the number of bookings on any given arrival date
```{r}
hotels %>%
  select(starts_with("arrival_"))
```
##Step 1: Construct Dates
```{r}
library(glue)
hotels %>%
  mutate(
    arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")
    ) %>% 
  relocate(arrival_date)
```
##Step 2: Count bookings by date
```{r}
hotels %>%
  mutate(arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")) %>%
  count(arrival_date)
```
##Step 3: Visualize bookings by date 
```{r}
hotels %>%
  mutate(arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")) %>%
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_line()
```
##Step 1. REVISED Construct dates "as dates"
```{r}
library(lubridate)
hotels %>%
  mutate(
    arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))
    ) %>% 
  relocate(arrival_date)
```
##Step 2. Count bookings per date
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date)
```
##Step 3a. Visualise bookings per date
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_line()
```
##Step 3b. Visualise using a smooth curve
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_smooth()
```



